---
title: "Chapter 1 - Overview"
author: "Morgan Grovenburg"
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

```{r libraries}
# Install packages only once
#install.packages("rstanarm")
# install.packages("tidyverse")
# install.packages("patchwork")

# Load libraries used (not part of base R)
library(rstanarm)
library(tidyverse)
library(patchwork)
```

```{r plot-func}
glm_plot <- function(data){
  data %>%
    ggplot(aes(growth, vote)) +
    geom_point() +
    geom_abline(intercept = coeff[1], slope = coeff[2]) +
    theme_classic() +
    ylim(20, 80)
}
```

# 1.2 Why learn regression? {.unnumbered}

```{r, results= "hide"}
hibbs <- read.table("hibbs.dat", header = TRUE)

M1 <- stan_glm(vote ~ growth, data=hibbs)
```

```{r}
coeff=coefficients(M1)
# equation of the line : 
eq = paste0("y = ", round(coeff[1],1), " + ", round(coeff[2],1), "*x")
plot(hibbs$growth, hibbs$vote, xlab="Average recent growth in personal income", ylab="Incumbent party's vote share", main = eq) +
  abline(coef(M1), col="gray")

print(M1)

p1 <- hibbs %>%
  glm_plot() + 
  labs(title = "Original")
```

# 1.8 Exercises {.unnumbered}

## 1.2 *Sketching a regression model and data*: Figure 1.1b shows data corresponding to the fitted line $y = 46.3 + 3.0x$ with residual standard deviation $3.9$, and values of $x$ ranging roughly from $0$ to $4$%. {.unnumbered}

### (a) Sketch hypothetical data with the same range of $x$ but corresponding to the line $y = 30 + 10x$ with residual standard deviation $3.9$. {.unnumbered}

```{r a-data, results = "hide"}
Ex1a <- tibble(vote = hibbs$vote+(30 - 46.3),
               growth = hibbs$growth)
Ex1a <- Ex1a %>%
  mutate(vote = vote+((10-3)*growth))

E1a <- stan_glm(vote ~ growth, data=Ex1a)
```

```{r a-plot}
coeff=coefficients(E1a)
# equation of the line : 
eq = paste0("y = ", round(coeff[1],1), " + ", round(coeff[2],1), "*x")
plot(Ex1a$growth, Ex1a$vote, main = eq) +
  abline(coef(E1a), col="gray")

print(E1a)

pa <- Ex1a %>%
  glm_plot() + 
  labs(title = "(a)")

p1 + pa
```

### (b) Sketch hypothetical data with the same range of $x$ but corresponding to the line $y = 30 + 10x$ with residual standard deviation $10$. {.unnumbered}

```{r b-data, results = "hide"}
#################
# Same as (a)
Ex1b <- tibble(vote = hibbs$vote+(30 - 46.3),
               growth = hibbs$growth)
Ex1b <- Ex1b %>%
  mutate(vote = vote+((10-3)*growth))
#################

res1b <- ((Ex1b$vote - (30 + 10*Ex1b$growth))*(10/3.9))

Ex1b <- Ex1b %>%
  mutate(vote = (30 + 10*Ex1b$growth)+res1b)

E1b <- stan_glm(vote ~ growth, data=Ex1b)
```

```{r b-plot}
coeff=coefficients(E1b)
# equation of the line : 
eq = paste0("y = ", round(coeff[1],1), " + ", round(coeff[2],1), "*x")
plot(Ex1b$growth, Ex1b$vote, main = eq) +
  abline(coef(E1b), col="gray")

print(E1b)

pb <- Ex1b %>%
  glm_plot() + 
  labs(title = "(b)")

pa + pb
```

## 1.5 *Goals of regression*: Give examples of applied statistics problems of interest to you in which the goals are: {.unnumbered}

Explain your answers

### (a) Forecasting/classification. {.unnumbered}

### (b) Exploring associations. {.unnumbered}

### (c) Extrapolation. {.unnumbered}

### (d) Causal inference. {.unnumbered}
